{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2020-11-20 documents/lessons_learned.tex
done

Minor errors in . Reproducible coding helps, but it would be much better if we had used standard software engineering best practices; red-teaming, unit testing on generated data, etc. It might also be helpful if the data itself are blinded against randomly generated controls - in many cases that's not possible, but it might be useful in some circumstances.

>>>>

Minor errors in . Reproducible coding helps, but it would be much better if we had used standard software engineering best practices; red-teaming, unit testing on randomly generated data, etc. It might also be helpful if the data itself are blinded against randomly generated controls - in many cases that's not possible, but it might be useful in some circumstances.
